Investigation of ant cuticle dataset using image texture analysis

### 2022-09-22 paper/main.tex
final touches
add initials

\author{%
    Noah Gardner\affil{1},
    John Paul Hellenbrand\affil{2},
    Anthony Phan\affil{1},
    Haige Zhu\affil{1},
    Zhiling Long\affil{4}, \\
    Min Wang\affil{3},
    Clint Penick\affil{2},
    and Chih-Cheng Hung\affil{1,}\corrauth
}%

@@

For the feasibility study in these ant image datasets, we tested the statistical
clustering methods and deep learning methods separately. Both K-means and
K-views were used for statistical clustering methods. The experiments may
indicate how well the statistical approach and deep learning networks will do in
this type of textural images. A pre-processing step of the dataset for the
statistical clustering methods is shown below. This pre-processing will
highlight some of characteristic features in textures, such as edge-like in the
image. This step is very useful in feeding the datasets to the K-views
algorithms. In order to classify an image with K-views or K-means in which we
count the number of pixels assigned to each cluster. A brief procedure for
K-views experiments is given below for training and classification.
\begin{description}
    \item[Step 1:] Pre-processing the dataset: apply the Gabor filter to
          transform the gray-scale ant image into four Gabor-filtered channels,
          subtract the gray-scale image from each channel, and take the absolute
          value of the resulting images. The theta θ parameters in the Gabor
          filters used are multiples of π/4 radians starting from 0 to π
          radians. The Gabor filter lambda λ parameter is equal to π.

>>>>

\author{%
    Noah Gardner\affil{1},
    John Paul Hellenbrand\affil{2},
    Anthony Phan\affil{1},
    Haige Zhu\affil{1},
    Zhiling Long\affil{4}, \\
    Min Wang\affil{3},
    Clint A. Penick\affil{2},
    and Chih-Cheng Hung\affil{1,}\corrauth
}%

@@

For the feasibility study in these ant image datasets, we tested the statistical
clustering methods and deep learning methods separately. Both K-means and
K-views were used for statistical clustering methods. The experiments may
indicate how well the statistical approach and deep learning networks will do in
this type of textural images. A pre-processing step of the dataset for the
statistical clustering methods is shown below. This pre-processing will
highlight some of characteristic features in textures, such as edge-like in the
image. This step is useful in feeding the datasets to the K-views algorithms. In
order to classify an image with K-views or K-means in which we count the number
of pixels assigned to each cluster. A brief procedure for K-views experiments is
given below for training and classification.
\begin{description}
    \item[Step 1:] Pre-processing the dataset: apply the Gabor filter to
          transform the gray-scale ant image into four Gabor-filtered channels,
          subtract the gray-scale image from each channel, and take the absolute
          value of the resulting images. The theta θ parameters in the Gabor
          filters used are multiples of π/4 radians starting from 0 to π
          radians. The Gabor filter lambda λ parameter is equal to π.
